Single-fluorophore orientation determination with multiview polarized illumination: modeling and microscope design

### 2017-11-09 paper/paper/paper.tex
Revised temporal resolution response. See Hari's Nov 9 email.

\documentclass[10pt]{article}
\usepackage[OE]{express}
\usepackage{float}
\usepackage{booktabs}
\usepackage{menukeys}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}

@@

We thank the reviewer for a valuable comment. We neglected to comment on the
ability of our designs to image the temporal evolution of a dipole, so we have
\hyperlink{temporal}{\color{urlblue} added several sentences} to address this
omission. In particular, we highlight that the brightness of the fluorophores is
the main factor that limits temporal resolution in these designs. We also
mention that the comparison we carried out in the manuscript only compare microscopes
with identical temporal resolution because we use a fixed sample irradiance.\\

@@

\hypertarget{temporal}{{\color{urlblue} We also chose to compare microscopes
    with a fixed irradiance incident on the sample so that all of the
    microscopes had the same temporal resolution. Given a fixed irradiance, the
    main factor that limits the temporal resolution of an orientation microscope
    is the brightness of the fluorophore (the rate of photon emission from the
    fluorophore). The orientation of bright fluorophores can be determined more
    quickly than dim fluorophores at the same level of accuracy because bright
    fluorophores generate measurements with a higher signal-to-noise ratio.}}

@@

Although we have only considered the orientation determination of fixed single
dipoles, polarized illumination techniques can be used to study the orientation
distribution of ensembles of dynamic dipoles \cite{mehta2016, backer2016}. In
future work we will investigate the ability of multiview polarized illumination
microscopes to estimate the orientation distribution of ensembles of dynamic
dipoles.

>>>>

\documentclass[10pt]{article}
\usepackage[OE]{express}
\usepackage{float}
\usepackage{booktabs}
\usepackage{menukeys}
\usepackage[normalem]{ulem}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\bs}[1]{\boldsymbol{#1}} 
\providecommand{\intinf}{\int_{-\infty}^{\infty}}

@@

We thank the reviewer for this valuable comment. We neglected to comment on the
ability of our designs to image dipoles that are rotating during the measurement
time, so we have \hyperlink{temporal}{\color{urlblue} added a paragraph} to
address this omission. We highlight that the modeling in this work only applies
to fixed dipoles, so estimating the orientation of rotating dipoles using these
methods will, in general, lead to incorrect estimates. However, if the dipole
rotates through a small solid angle during the measurement time, the models used
in this paper will give a slightly biased estimate of the average orientation of
the dipole. The precision results in this paper for fixed dipoles apply to
rotating dipoles if the dipoles rotate through a small solid angle during the
measurement time. If the dipoles rotate through a large solid angle during the
measurement time, then further modeling is required to
accurately estimate the dipole orientation.\\

@@

% \hypertarget{temporal}{{\color{urlblue} We also chose to compare microscopes
%     with a fixed irradiance incident on the sample so that all of the
%     microscopes had the same temporal resolution. Given a fixed irradiance, the
%     main factor that limits the temporal resolution of an orientation microscope
%     is the brightness of the fluorophore (the rate of photon emission from the
%     fluorophore). The orientation of bright fluorophores can be determined more
%     quickly than dim fluorophores at the same level of accuracy because bright
%     fluorophores generate measurements with a higher signal-to-noise ratio.}}

@@

\hypertarget{temporal}{{\color{urlblue} The models in this paper only consider
    estimating the orientation of fixed dipoles, but real dipoles change their
    orientation during measurement. Therefore, it is necessary to comment on the
    applicability of our results to dynamic dipoles. In general, using the
    models in this paper to estimate the orientation of rotating dipoles will
    lead to incorrect results. However, if a dipole rotates through a small
    solid angle during the measurement, the models in this paper will give a
    precise and slightly biased estimate of the average orientation of the
    dipole. The results in this paper apply to the precision of our estimates
    for the average dipole orientation of rotating dipoles, but the direction
    and size of the bias has not been characterized in detail. In future work we
    will model dynamic dipoles and attempt to estimate the average dipole
    orientation and the dipole's orientation distribution. Single-view polarized
    illumination techniques have already been used to study the orientation
    distribution of ensembles of dynamic dipoles \cite{mehta2016, backer2016},
    but multiview polarized illumination microscopes have not been investigated
    for this purpose.}}

{\color{red}\sout{Although we have only considered the orientation determination
    of fixed single dipoles, polarized illumination techniques can be used to
    study the orientation distribution of ensembles of dynamic dipole. In future
    work we will investigate the ability of multiview polarized illumination
    microscopes to estimate the orientation distribution of ensembles of dynamic
    dipoles.}}
